Introducing Statistical Design of Experiments to SPARQL Endpoint Evaluation

### 2013-05-05 exp1/iswc2013.tex
stubs
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@500 43ef1190-90fd-4dd7-a769-d0121f02b80e
small changes
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@502 43ef1190-90fd-4dd7-a769-d0121f02b80e

As the focus of this paper is didactical, the actual measurements are
much simpler than what has been used in benchmarking. We have used the
dataset of \cite{mxro:Morsey2011DBpedia}, but only consider the
smallest of their datasets (that we found to me more than 15
MTriples). Moreover, we have taken subsets of that dataset by using
the last 1 or 2 MTriples their file.

@@

The experimentation is implemented in R\todo{ref}, which is a free
software environment for statistical computing and graphics. Necessary
tools for DoE has been implemented by the R community in packages
called DoE.base, BsMD and FrF2. The experiments are run on a third
computer in a 1 gigabit LAN with the two experiment hosts.  As
response variable, we have chosen to use the time from the namespace
server lookup to the data has been transferred. This choice is
somewhat arbitrary, many other response variables could be chosen, and
indeed, future work should explore multi-variable responses, but for
simplicity, we think this reflects the total amount of work done by
the SPARQL endpoint well. For the measurements, we have chosen to use
the RCurl package, which is a thin wrapper around the curl
library. Curl has  good facilities for timing requests, and so
we rely on its measurements.

@@

\section{Conclusion}

>>>>

As the focus of this paper is didactical, the actual measurements are
much simpler than what has been used in benchmarking. We have used the
dataset of DBPedia SPARQL Benchmark\cite{mxro:Morsey2011DBpedia}, but only consider the
smallest of their datasets (that we found to be more than 15
MTriples). Moreover, we have taken subsets of that dataset by using
the last 1 or 2 MTriples from their file.

@@

The experimentation is implemented in R\todo{ref}, which is a free
software environment for statistical computing and graphics. Necessary
tools for DoE has been implemented by the R community in packages
called DoE.base, BsMD and FrF2. The experiments are run on a third
computer in a 1 gigabit LAN with the two experiment hosts.  As
response variable, we have chosen to use the time from the namespace
server lookup to the data has been transferred. This choice is
somewhat arbitrary, many other response variables could be chosen, and
indeed, future work should explore multi-variable responses, but for
simplicity, we think this reflects the total amount of work done by
the SPARQL endpoint well. For the measurements, we have chosen to use
the RCurl package, which is a thin wrapper around the curl
library. Curl has well developed facilities for timing requests and
responses, and so we rely on its measurements.

@@

\section{Discussion}

\paragraph{Summary and hypothesis test}

\paragraph{Strategy for evaluating experiment}\todo{Say something
  about examining variance} \todo{Say something about drilling down in
  factors} \todo{Say something about spreading levels}

\paragraph{Fold-over}

\section{Future Work}

\section{Conclusions}
